\MakeUppercase{Layered $H$-Partitions of $k$-Planar Graphs} \thanks{This work was partly funded by NSERC and MRI.}

### 2019-05-12 k-planar.tex
Added a reminder about David's suggestions

  \item \proplabel{ancestor-boundary} For each non-root node $x\in V(T)$, there exists a partition of $V(F_x)$ into $g\le 3$ sets $P_1,\ldots,P_g$ such that, for each $i\in\{1,\ldots,g\}$, either:
  \begin{compactenum}
    \item $F[P_i]$ is a path that is contained in $Y_a$ for some $K$-ancestor $a$ of $x$;
    \item $F[P_i]$ is a cycle and there exists an edge of $P_i$ whose removal produces a path that is contained in $Y_a$ for some $K$-ancestor $a$ of $x$; or 
    \item $F[P_i]$ is a path or cycle in $F_{r_K}$.
  \end{compactenum}
  \item \proplabel{partition} $\{Y_x : x\in V(K)\}$ is a partition of $V(\Delta)\setminus\{r\}\setminus V(F_{r_K})$.
\end{enumerate}

@@

\section{$1$-Planar Graphs}
\seclabel{1-planar}

>>>>

  \item \proplabel{ancestor-boundary} For each non-root node $x\in V(T)$, there exists a partition of $V(F_x)$ into $g\le 3$ sets $P_1,\ldots,P_g$ such that, for each $i\in\{1,\ldots,g\}$, either:
  \begin{compactenum}
    \item $F[P_i]$ is a path that is contained in $Y_a$ for some $K$-ancestor $a$ of $x$;
    \item $F[P_i]$ is a cycle and there exists an edge of $F[P_i]$ whose removal produces a path that is contained in $Y_a$ for some $K$-ancestor $a$ of $x$; or 
    \item $F[P_i]\subseteq F_{r_K}$.
  \end{compactenum}
  \item \proplabel{partition} $\{Y_x : x\in V(K)\}$ is a partition of $V(\Delta)\setminus\{r\}\setminus V(F_{r_K})$.
\end{enumerate}

@@

\noindent
\framebox{
\begin{minipage}{\textwidth}
  \note{DW}{%
    I think we need to define layered treewidth, and
    give the result of Dujmovic-Eppstein-Wood that (g,k)-planar graphs
    have O(gk)  layered treewidth. This is the best previous structural
    description of k-planar graphs. State that layered partitions are
    richer than  layered treewidth, and lead to O(1) bounds on non-rep
    chromatic number and queue-number, instead of O(log n) bounds via
    layered treewidth.

    I also think we should give explicit upper bounds on non-rep chromatic
    number for k-planar graphs, and also for queue-number (especially if
    they improve the bound in the FOCS / J.ACM paper).

    I think we should think about generalising the new theorem for
    (g,k)-planar graphs.

    We should add corollaries for d-map graphs, since they are $d^2$-planar.
    }
\end{minipage}
}
\section{$1$-Planar Graphs}
\seclabel{1-planar}
